APPM report - Draft

### 2023-01-04 paper_version/main.tex
minor change

We employ the finite volume method (FVM) to discretize the Euler system. The Euler
equations (\ref{equ:euler_}) can be cast into the form of conservation law with source
terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for a vector of $m$
conservative variables,
$\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times [0,T], \mathbb{R}^{3 \times m})$ is the flux
function, and $\mathbf{RHS} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ is the source
term.. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
$\mathbf{U} := [n, n\mathbf{u}, ne]$.

>>>>

We employ the finite volume method (FVM) to discretize the Euler system. The Euler
equations (\ref{equ:euler_}) can be cast into the form of conservation law with source
terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ stands for $m$
conservative variables;
$\mathbf{f}(\mathbf{U}) : \Omega \times [0,T] \rightarrow \mathbb{R}^{3 \times m}$ is the flux
function depending on $\mathbf{U}$; $\mathbf{RHS} : \Omega \times [0,T] \rightarrow \mathbb{R}^m$ is the source
term. In the case of the full 3D Euler equations (\ref{equ:euler_rescaled}), $m = 5$ and
$\mathbf{U} := [n, n\mathbf{u}, ne]$.
